Assessing primitives performance\\ on multi-stage execution

### 2018-05-16 paper.tex
fix after some comments

The Slang implementation is written inside the interpreter and has access to the full interpreter APIs. Since the same primitive index \sd{no idea what is it} is used for the primitive with two or three arguments, the primitive needs to deal with both cases in a way that the common case is efficient. The primitive is now part of the core of the VM, it cannot be easily added or removed as plugin primitives, but it is simpler to read and write. This primitive follows the new specification, the full code is available in Appendix \ref{SlangAppendix}.

@@

\subsection{Micro-benchmarks}

@@

\paragraph{Optimization potential on large strings comparison.}
The plugins come with an overhead \sk{not an overhead when it comes to inlining. Just not optimized. need rephrasing} due to the cross-file inlining and the passage through an InterpreterProxy, like said in Section~\ref{sec:implem_cmp}. This is one of the factor explaining the performance gap between these versions and the Slang and Slang+JIT ones.
When it comes to comparing large strings (100 characters and more), the execution time is mainly spent in the comparison loop (Figure~\ref{fig:Asm}). However, the switch overhead is still noticeable in the PureSlang implementation when strings of 100 characters are compared: PureSlang is 15.8 times faster than Baseline while Slang+JIT is 16.8 times faster than Baseline. This is not the case anymore on 1000-characters strings.
This last observation only applies to the GCC results: the code generated by the LLVM compiler induces a longer execution time, as explained in the next paragraph.

>>>>

The Slang implementation is written inside the interpreter and has access to the full interpreter APIs. This primitive takes with two or three arguments and needs to deal with both cases in a way that the common case is efficient. The primitive is now part of the core of the VM, it cannot be easily added or removed as plugin primitives, but it is simpler to read and write. This primitive follows the new specification, the full code is available in Appendix \ref{SlangAppendix}.

@@

\subsection{Micro-benchmarks} \sk{Results?}

@@

\paragraph{Optimization potential on large strings comparison.}
The plugins come with an overhead due the use of an interface. Besides, cross-file inlining is not performed for plugins, like said in Section~\ref{sec:implem_cmp}. These are some of the factors explaining the performance gap between these versions and the Pure Slang and Slang+JIT ones.
When it comes to comparing large strings (100 characters and more), the execution time is mainly spent in the comparison loop (Figure~\ref{fig:Asm}). However, the switch overhead is still noticeable in the PureSlang implementation when strings of 100 characters are compared: PureSlang is 15.8 times faster than Baseline while Slang+JIT is 16.8 times faster than Baseline. This is not the case anymore on 1000-characters strings.
This last observation only applies to the GCC results: the code generated by the LLVM compiler induces a longer execution time, as explained in the next paragraph.
